\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
mi parte

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications (see \cite{bib:uquad} for example). In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

In equation \refp{eq:calib_temp}, $N$ is the number of samples took, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature) and $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp}. This last vector includes the variable that we want to estimate.\\

\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. However the offset values obtained differ considerably from the information of the datasheet (see \cite{bib:acc_data}), where is declared that the 0g output deviation from ideal is $\pm 35 mg$ for axes $x$ and $y$ and $\pm 40mg$ for axis $z$. This means that the offsets should be less than $11$ bits, therefore a difference between the results obtained in the calibration and what is stated in the datasheet of the sensor exists.\\

@@

\begin{equation}
\mu_\omega = 6.67 \times 10^{-3} rad/s\, \sigma_\omega = 7.4 \times 10^{-3} rad/s
\end{equation}

The mean and the standard deviation obtained both correspond to approximately $6$ bits errors.

@@

\section{Conclusion}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{ieeetr} 
\bibliography{../biblio}
% \begin{thebibliography}{1}

>>>>

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications. In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

In equation \refp{eq:calib_temp}, $N = 22740$\footnote{This number is not needed to be this big, yet all the data of the cooling process was used (see figure \ref{fig:bajada}).} is the number of samples took, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature) and $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp}. This last vector includes the variable that we want to estimate.\\

It is important to clarify that to perform a perfect temperature compensation, variations of temperatures should be produced with the sensors in different orientations. However, the one that is the most important is with the platform in horizontal position with the $z$ axis pointing ``up''. This is because this particular position is the main operating situation in the application for which this calibration method was thougth.
\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. However the offset values obtained differ considerably from the information of the datasheet (see \cite{bib:acc_data}), where is declared that the 0g output is $\pm 150 mg$ for axes $x$ and $y$ and $\pm 250mg$ for axis $z$. This correspond to offsets of $39$ bits maximum for $x$ and $y$, and $64$ for $z$. The results obtained are consistent with what is declared in the datasheets.

@@

\begin{equation}
\mu_\omega = -3.50 \times 10^{-3} rad/s\, \sigma_\omega = 4.57 \times 10^{-2} rad/s
\end{equation}

The mean and the standard deviation obtained correspond to an error of approximately $3$ and $30$ bits respectively.

@@

\section{Conclusion}
A very easy, fast and low cost procedure for calibrating inertial measurement sensors was 
presented. It combines nonlinear least squares adjustment of sensor parameters and misalignment 
angles, a very simple and inexpensive experimental setup, and a simple adjustment of temperature bias' drift.

It was successfully implemented and tested to perform the calibration of the sensors unit (IMU) 
used to estimate the state variables of a quadrotor. Experimental results show a very precise determination of the acceleration and angular velocity. This precision is achieved also during a wide variation of operating temperature of the sensors. This allows satisfactory estimation for flight control in a wide range of operating conditions.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{ieeetr} 
\bibliography{../biblio}
% \begin{thebibliography}{1}
